Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-12-15 main.tex
Report on With-me-ness measurements

\begin{table}[ht!]
\centering
\caption{\small Field studies conducted within the project}
\label{studies}
\footnotesize
\begin{tabular}{@{}lp{4cm}p{2.2cm}p{2cm}l@{}}
\toprule
{\bf Study}        & {\bf Type}                               & {\bf Avg. duration}    & {\bf Children \#}                     & {\bf Ages} \\ \midrule
{\it School A (1)} & Unstructured group interaction at school & 16 min/group           & 4 $\times$ 8 children                 & 6-7        \\
{\it School B}     & Individual/Pair interaction at school    & 11 min/group           & 7 (individual) + 7 $\times$ 2 (pairs) & 7-8        \\
{\it School C}     & Pair interaction at school               & 26 min/group           & 7 $\times$ 2                          & 5-6        \\
{\it School A (2)} & Individual interaction at school         & 18 min                 & 6                                     & 5-6        \\ \midrule
{\it Surgery}      & Individual interaction at surgery        & 3 sessions $\times$ 1h & 8                                     & 6-8        \\ \midrule 
{\it Vincent}      & Case-study, spanning over 4 weeks        & 4 weeks $\times$ 1.5h  & 1                                     & 6          \\
{\it Thomas}       & Case-study, spanning over 4 weeks        & 4 weeks $\times$ 1h    & 1                                     & 5          \\ \bottomrule
\end{tabular}
\end{table}

@@

From a technical perspective, the system achieves an acceptable level of
reliability and allow a technically sound autonomous interaction. For instance,
during the second school study (\textit{Florimont}), the robot withstood
interactions which lasted for a total of 160 minutes.  During this time the
robot wrote 335 letters, 152 of which in response to demonstrations received
from the 21 children. Technical intervention was only required for the three
instances that the robot fell during that day.  Otherwise, the technical
components of the system operated autonomously and as expected over the
sessions.

@@

Factually, the children engaged into the teaching activity: in the
\textit{Florimont} study, for instance, they demonstrated an average of
10.9 demonstration letters (SD = 4.4) for an average session duration of 11 minutes.
In 9 out of the 14 sessions (64\%), the robot
received demonstration letters even \emph{after} reaching the final stage of the
interaction, suggesting an intrinsic motivation to further engage in the
interaction.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.9\linewidth]{engagement}
    \caption{\small Engagement level of one child, manually annotated by two judges
        over a 13 min long interaction (Cronbach’s alpha test: $\alpha = .82$,
        good inter-judge agreement). 0 means ``complete disengagement from the
        task'', 6 means ``full engagement''. The vertical lines represent activity
    switches between handwriting teaching and story-telling (used as a
    distruber).}
    \label{engagement_level}
\end{figure}

We also conducted a qualitative assessment of the engagement levels during
several interaction sessions (studies \textit{Haut-Lac} and \textit{ISG 2}).
While the overall engagement was high, Figure~\ref{engagement_level} shows an
example of a child with moderate level of engagement. On-going research in our
group aims at assessing such engagement levels in real-time, so that the robot
can address possible disengagement (by changing/adapting its physical behaviour,
by switching to different activities, etc.)

We also performed further qualitative assessment of engagement over longer
interaction periods: two 4-weeks long case studies with one child at a time have
been conducted so far, the first one (\emph{Vincent}) focusing on
\emph{engagement on the long run}, the second one (\emph{Thomas}) looking at
\emph{acceptance and impact in a real therapeutic context}.

>>>>

\begin{table}[ht!]
\centering
\caption{\small Field studies conducted within the project}
\label{studies}
\footnotesize
\begin{tabular}{@{}lp{4cm}p{2.2cm}p{2cm}l@{}}
\toprule
{\bf Study}        & {\bf Type}                               & {\bf Avg. duration}    & {\bf Children \#}                     & {\bf Ages} \\ \midrule
{\it School A (1)} & Unstructured group interaction at school & 16 min/group           & 4 $\times$ 8 children                 & 6-7        \\
{\it School B}     & Individual/Pair interaction at school    & 11 min/group           & 7 (individual) + 7 $\times$ 2 (pairs) & 7-8        \\
{\it School C}     & Pair interaction at school               & 26 min/group           & 7 $\times$ 2                          & 5-6        \\
{\it School A (2)} & Individual interaction at school         & 20 min                 & 6                                     & 5-6        \\ \midrule
{\it Surgery}      & Individual interaction at surgery        & 3 sessions $\times$ 1h & 8                                     & 6-8        \\ \midrule 
{\it Vincent}      & Case-study, spanning over 4 weeks        & 4 weeks $\times$ 1.5h  & 1                                     & 6          \\
{\it Thomas}       & Case-study, spanning over 4 weeks        & 4 weeks $\times$ 1h    & 1                                     & 5          \\ \bottomrule
\end{tabular}
\end{table}

@@

From a technical perspective, the system achieves an acceptable level of
reliability and allow a technically sound autonomous interaction. For instance,
during the second school study (\textit{School B}), the robot withstood
interactions which lasted for a total of 160 minutes.  During this time the
robot wrote 335 letters, 152 of which in response to demonstrations received
from the 21 children. Technical intervention was only required for the three
instances that the robot fell during that day.  Otherwise, the technical
components of the system operated autonomously and as expected over the
sessions.

@@

Factually, the children engaged into the teaching activity: in the
\textit{School B} study, for instance, they demonstrated an average of
10.9 demonstration letters (SD = 4.4) for an average session duration of 11 minutes.
In 9 out of the 14 sessions (64\%), the robot
received demonstration letters even \emph{after} reaching the final stage of the
interaction, suggesting an intrinsic motivation to further engage in the
interaction.

%\begin{figure}[ht!]
%    \centering
%    \includegraphics[width=0.9\linewidth]{engagement}
%    \caption{\small Engagement level of one child, manually annotated by two judges
%        over a 13 min long interaction (Cronbach’s alpha test: $\alpha = .82$,
%        good inter-judge agreement). 0 means ``complete disengagement from the
%        task'', 6 means ``full engagement''. The vertical lines represent activity
%    switches between handwriting teaching and story-telling (used as a
%    disturber).}
%    \label{engagement_level}
%\end{figure}

\begin{table}[h!]
    \centering
    \caption{\textbf{Levels of with-me-ness}. Percentage of interaction time
        during which the child was effectively focusing his/her attention on the
        task. The six children are those from the second study at School A.
        Interaction duration: M = 19.6 min, SD = 1.58. Results
        taken from~\cite{lemaignan2016realtime}.}

    \begin{tabular}{p{1cm}cccccccc}
        \toprule
        Child & 1 & 2 & 3 & 4 & 5 & 6 & {\bf M} & {\it SD} \\
        \midrule
        $\mathcal{W}$ & 79.4\% & 81.6\%  & 90.5\% & 87.9\% & 90.7\% & 80.9\% & {\bf 85.2\%} & {\it 5.1} \\ 
        \bottomrule
    \end{tabular}
    \label{tab:results-with-me-ness}
\end{table}

We also conducted a quantitative assessment of the engagement levels of the
children. Table~\ref{tab:results-with-me-ness} reports the levels of
\emph{with-me-ness} of the children during the second study at school A.
\emph{With-me-ness} is a quantifiable precursor of engagement: it measures the
percentage of time spent by the child focusing onto the task at end. It was
first devised in the context of computer-supported
learning~\cite{sharma2014me}, and we have previously studied its applicability to
human-robot interaction and formalized the exact methodology
in~\cite{lemaignan2016realtime}\footnote{Note that with-me-ness is a metric that
allows real-time computation by the robot itself: while we did not yet make
use of it, it would allow the robot to detect possible disengagements, and
eventually address them by adapting its physical behaviour, switching to
different activities, etc.}.

The average with-me-ness is well above 80\%, and confirms that the children
where very much engaged into these 20 minutes of interaction with the robot,
paying close attention to the task.

The other three experiments (the group study at the surgery and the two
case-studies) provide further qualitative assessment of engagement over longer
interaction periods. In particular, as reported hereafter, the two 4-weeks long
case studies that have been conducted so far show that our system can sustain
children' engagement over durations (5 hours) that are closer to what is
expected to have an impact in a real therapeutic context.
